Meta-analysis

### 2020-05-26 04_MetaAnalysis.Rmd
spelling
Fixed on my ipad

   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
   # let's test to make sure
   if (max(outer(
      X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      FUN = "-"
   )) > 0) {
      message(
         paste(
            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
            "i =",
            i
         )
      )
      next()
   } else{
      message(
         paste(
            i,
            "iterations: ",
            "imputed variances now show no significant distances :)\n Now adding variances to data "
         )
      )

>>>>

   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
   # let's test to make sure
   if (max(outer(
      X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      FUN = "-"
   )) > 0) {
      message(
         paste(
            "\nWarning!!: Imputed yield errors bestow significant differences on the means.\n",
            "The original experiment reported no significant differences in the yields, therefore values will be discarded and the imputation function run again - iteration number:",
            "i =",
            i
         )
      )
      next()
   } else{
      message(
         paste(
            i,
            "iterations: ",
            "imputed variances now show no significant distances :)\n Now adding variances to data "
         )
      )
